Case Study: 16S microbiome data (Baxter et al., 2016)

### 2018-10-18 datasets/microbiome/microbiome-baxter.Rmd
Add results plots for mean abunandance covariate
Add uninformative covariate comparison to CRC genus level

gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(sbdir, "baxter-genus-benchmark.rds")
gns_bench_file_log_ubiquity <- file.path(sbdir, "baxter-genus-log-ubiquity-benchmark.rds")
gns_bench_file_abun <- file.path(sbdir, "baxter-genus-mean-abun-benchmark.rds")
```

@@

@@

@@

@@

```{r}
plotMethodRanks(c(otu_bench_file, otu_bench_file_log_ubiquity, 
                  gns_bench_file, gns_bench_file_log_ubiquity,
                  gns_bench_file_abun), 
                colLabels = c("OTU", "OTU - log", "Genus", "Genus - log",
                              "Genus - abun"), 
                alpha = 0.10, xlab = "Comparison")
```

>>>>

gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(sbdir, "baxter-genus-benchmark.rds")
gns_bench_file_log_ubiquity <- file.path(sbdir, "baxter-genus-log-ubiquity-benchmark.rds")
gns_bench_file_abun <- file.path(sbdir, "baxter-genus-mean-abun-benchmark.rds")
gns_bench_file_uninf <- file.path(sbdir, "baxter-genus-mean-uninf-benchmark.rds")
```

@@

Add random (uninformative) covariate to test at the genus level.

```{r}
set.seed(72664)
res$rand_covar <- rnorm(nrow(res))
```

@@

### Random

```{r, baxter-uninf-hist, fig.width=10, fig.height=3.2}
strat_hist(res, pvalue="pval", covariate="rand_covar", maxy=8, binwidth=0.05)
```

```{r, baxter-uninf-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(res, pvalue="pval", covariate="rand_covar")
```

@@

## Multiple-Testing Correction - Random

Let's use `rand_covar` as our `ind_covariate`.

```{r, baxter-genus-labelcovariate-uninf}
res <- dplyr::mutate(res, ind_covariate = rand_covar)
```

```{r, baxter-genus-sb-uninf, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_uninf)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_uninf)
} else {
    sb <- readRDS(gns_bench_file_uninf)
}
```
## Benchmark Metrics - Random

```{r, baxter-genus-uninf-metrics, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, baxter-genus-uninf-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

```{r, baxter-genus-uninf-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r}
plotMethodRanks(c(otu_bench_file, otu_bench_file_log_ubiquity, 
                  gns_bench_file, gns_bench_file_log_ubiquity,
                  gns_bench_file_abun, gns_bench_file_uninf), 
                colLabels = c("OTU", "OTU - log", "Genus", "Genus - log",
                              "Genus - abun", "Genus - uninf"), 
                alpha = 0.10, xlab = "Comparison")
```
